Deriving a precise Newtonian equation for the time it takes two separated bodies in an isolated system to collide due to the gravitational force

### 2022-10-30 paper/draft.tex
cleanup

Now we can take the reciprocal of this, because we want to solve for $t$ at the left side, where $dt$ is currently the denominator. Also rearranging it slightly gives

@@

Our main problem now consists of solving the integral on the right side of the equation, which we will do in the next section

@@

And therefore, if we define $\Delta s = R_i - R_f$, so the change in distance for which we want to calculate the time it takes to get there, our final result becomes

@@

print('With a dt of ' + str(dt) + ' our simulation time in seconds is')
print(t)

print('According to our full final equation, the following should be the time in seconds:')
print(- math.sqrt(r_i / (2*gravitational_constant*(m_1 + m_2))) * (r_i * (math.atan(math.sqrt(r_f / delta_s)) - 0.5 * math.pi) - math.sqrt(r_f * delta_s)))

print("And according to the Kepler equation, we get:")
print(math.pi * math.sqrt(pow(r_i, 3) / (8 * gravitational_constant * (m_1 + m_2))))
\end{lstlisting}
We get the following output while running the script:

\end{document}

>>>>

Now let us take the reciprocal of this because $dt$ is currently in the denominator and we want to solve for $dt$ so we can integrate for time. Additionally, rearranging it slightly gives

@@

Our main problem now consists of solving the integral on the right side of the equation, which we will attempt in the next section

@@

If we define $\Delta s = R_i - R_f$, the change in distance for which we want to calculate the time it takes to get there, our final result becomes

@@

    print("dt: " + str(round(dt, 6)))
    print("simulation time: " + str(round(t, 6)))

    equation_time = - math.sqrt(r_i / (2 * gravitational_constant * (m_1 + m_2))) * (
                r_i * (math.atan(math.sqrt(r_f / delta_s)) - 0.5 * math.pi) - math.sqrt(r_f * delta_s))
    print("equation time: " + str(round(equation_time, 6)))

    kepler_time = math.pi * math.sqrt(pow(r_i, 3) / (8 * gravitational_constant * (m_1 + m_2)))
    print("kepler time: " + str(round(kepler_time, 6)))    
\end{lstlisting}
We get the following output while running the script:
\begin{lstlisting}
    dt: 0.001000
    simulation time: 5521437.476000
    equation time: 5521437.475077
    kepler time: 5522200.716264
\end{lstlisting}
So it takes $5521437$ seconds, or 63 days 21 hours and almost 44 minutes, for the earth to crash into the sun. Running the program with an increasingly small $dt$, it is also very convincing that the simulation time actually converges to the time of our equation. Also, you can see that the time difference by using the Kepler's equation simplification is quite large in terms of seconds. In fact it is off by approximately 763 seconds. 
\end{document}
